% https://tex.stackexchange.com/a/346567
\documentclass{beamer}
\usetheme{Berkeley} 

\usepackage{xpatch}

\makeatletter
\patchcmd\beamer@@tmpl@frametitle{\insertframetitle}{\insertsection\space-- \insertframetitle}{}{}
\makeatother


\begin{document}
\section{Introduction}
\begin{frame}[shrink]
\frametitle{Global burden by World Bank}
Global burden of STIs and their consequences (World Bank)
\begin{itemize}
\item among world’s most common diseases, with an annual incidence exceeded only by diarrheal diseases, malaria, and lower respiratory diseases. 
\item Due to their high \textbf{prevalence}, particularly in developing settings, STIs result in substantial productivity losses for individuals and communities. %, particularly where the majority of the population is under 40 years of age. 
\item In developing countries, STIs are among the leading causes of disability-adjusted life years (DALYs) lost for \textbf{women} of reproductive age. 
\item Every day, 1M \textbf{acquire} a new STI, and more than 340 million new cases of curable STIs occur throughout the world each year. 
Adolescents and young adults have the highest rates of curable STIs -- up to 1 in 20 adolescents develop a new STI each year. 
\item \textbf{Untreated} bacterial STIs in women - PID in 40\% infections, 1/3 in infertility, ...
\item \textbf{Perinatal deaths}. Syphilis - one of most common causes of adverse pregnancy outcomes globally, 1.5M deaths/year. 
\item \textbf{Chronic liver disease and death}. HBV, 1/40 deaths of adults globally per year. 
\item \textbf{Cervical cancer and death}. Most common cause of cancer mortality among African women. About 0.24 M/year mortality in resource poor seettings. 
\item \textbf{Prevention}. Vaccines, .... Antibiotics for many STIs. Antivirals in HIV and HSV-2.  
\end{itemize}
\end{frame}
\end{document}
